---
title: "RMarkdown Practice"
author: 'Andrew Peters'
output: html_document
---

# Syntax practice!

###### This is how you control the size of headers.
###### Fun fact: an alternate name for the pound-sign is the octothorpe

Here is an an equation with pi and exponents  
$area=\pi*r^2$  


>This is a block quote, announcing a pair of lists

* unordered list
* same list, item 1
  + sub-item 1


1. ordered list item 1
2. item 2


~~This is a completely original set of examples~~  
**Below** is the link with these examples  
[link](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)  

### Here is a midsized header, announcing a table.  


### Things I wasn't able to get working:  
* Inserting images  
* Creating tables within the rmarkdown text editor  

# Embedding code:  


```{r, eval = TRUE, echo=FALSE}
dim(iris)
```

## Embedding external code:  
First, read in the r file using the "read_chunk()" command in a chunk of code like so:  

```{r}
knitr::read_chunk('ExternalChunkExample.R')  
```

then embed code asking for the chunk by it's label (which must be added in R file), like so:  

```{r CountyIncomeHead}
```
